Summary Tables

### 2020-02-20 summary_tables_outcomes.Rmd
Fix typo
Use true_dist instead
Add whw and nov together, and also produce all cities wide injury risk per 100k kms

for(city in cities){
  if (!city %in% c('buenos_aires', 'mexico_city')){
    for (cs in names(io$accra$outcomes$whw)[1]){
      print(kable(format(round(io[[city]]$outcomes$whw[[cs]]$whw)), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")
    }

@@

for(city in cities){
  if (!city %in% c('bogota', 'vizag')){
    for (cs in names(io$accra$outcomes$whw)[1]){
      print(kable(format(round(io[[city]]$outcomes$whw[[cs]]$nov)), caption = paste('NOV ', cs, ' matrix for ', city)))
      cat("\n")
    }

@@

### Change in deaths due to injury per 100,000K

@@

@@

@@

      td4 <- io[[city]]$dist %>% filter(stage_mode %in% td3$mode) %>% dplyr::select(stage_mode, cs)

@@

      # print(td4)
    }
    print(kable(el, caption = city))
    cat("\n")
    #kable(print(el), caption = city)
  #}

@@

>>>>

for(city in cities){
  if (!city %in% c('buenos_aires', 'mexico_city')){
    for (cs in names(io$accra$outcomes$whw)){
      print(city)
      td1 <- (io[[city]]$outcomes$whw[[cs]]$whw) %>% as.data.frame() %>% tibble::rownames_to_column("mode")
      td3 <- td1
      if (!is.null(io[[city]]$outcomes$whw[[cs]]$nov)){
        td2 <- t(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame()
        td2$mode <- 'NOV'

        td3 <- plyr::rbind.fill(td1, td2)
      }
      td3 <- td3 %>% mutate(rowSum = rowSums(.[2:ncol(td3)], na.rm = T))
      td3 <- td3 %>% janitor::adorn_totals("row")
      td3[, 2:ncol(td3)] <- round(td3[, 2:ncol(td3)], 2)

        print(kable(format(td3, scientific = F), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")
    }

@@

for(city in cities){
  if (!city %in% c('bogota', 'vizag')){
    for (cs in names(io$accra$outcomes$whw)){
      print(kable(format(round(io[[city]]$outcomes$whw[[cs]]$nov)), caption = paste('NOV ', cs, ' matrix for ', city)))
      cat("\n")
    }

@@

### Change in deaths due to injury per 100,000 km

@@

overall_el <- list()

@@

  #city <- 'delhi'

@@

      td4 <- io[[city]]$true_dist %>% filter(stage_mode %in% td3$mode) %>% dplyr::select(stage_mode, cs)

@@

      # print(td4)
    }
    print(kable(el, caption = city))

    td <- el %>% dplyr::select(-contains('count'))
    names(td)[2:ncol(td)] <- paste(names(td)[2:ncol(td)], city, sep = "_")

    overall_el[[city]] <- td

    cat("\n")
    #kable(print(el), caption = city)
  #}

@@

### Change in deaths due to injury per 100,000 km across cities

```{r inj_100k_all_cities = "asis"}
require(tibble)

td <- overall_el %>% purrr::reduce(full_join, by = "stage_mode") %>% as.data.frame()

td <- td %>% dplyr::select(stage_mode, sort(names(.)))

print(kable(format(td, scientific = F), caption = paste('Injury per 100k across all cities')))
